Capstone Movielens Report

### 2025-10-26 reports/capstone-movielens.site/05.appendix.Rmd
Fix for function: msg.glue.

Builds a message string from the template passed in the [msg_template](#func.msg.glue.args.msg_template) argument using the format element specified by the following arguments:

  - [arg.name](#func.msg.glue.args.arg.name): name of the element;

  - [arg](#func.msg.glue.args.arg): the element value.

@@

::: { #func.msg.glue.args.msg_template .sidebar }
  - **msg_template:** Message template (or format string), i.e., any (possibly multiline) string containing at least one occurrence of a substring specified by the [arg.name](#func.msg.msg.glue.args.arg.name) argument.

@@

::: { #func.msg.glue.args.arg.name .sidebar }
  - **arg.name:** Substring to replace in the message template passed in the [msg_template](#func.msg.msg.glue.args.msg_template) argument with the value specified in the [arg](#func.msg.msg.glue.args.arg) argument.
:::

::: { #func.msg.glue.args.arg .sidebar }
  - **arg:** Value to replace the format elements represented by the substring specified by the [arg.name](#func.msg.glue.args.arg.name) argument in the message template passed in the [msg_template](#func.msg.glue.args.msg_template) argument.

@@

This function internally calls [stringr::str_glue](https://www.rdocumentation.org/packages/stringr/versions/1.5.0/topics/str_glue) and [stringr::str_replace_all](https://www.rdocumentation.org/packages/stringr/versions/1.5.0/topics/str_replace) `R` functions to format a string from the template using the format value passed in the [msg_template](#func.msg.glue.args.msg_template) and [arg](#func.msg.glue.args.arg)  arguments, respectively.

@@

A glue object, as created by [glue::as_glue()](https://glue.tidyverse.org/reference/glue.html) from the character vector produced by the [stringr::str_replace_all()](https://www.rdocumentation.org/packages/stringr/versions/1.5.0/topics/str_replace).

>>>>

Creates a [glue::glue](https://glue.tidyverse.org/reference/glue.html) object from the template passed in the [msg_template](#func.msg.set_arg.args.msg_template) argument, using the value specified by the [arg](#func.msg.set_arg.args.arg) argument to replace all the occurrences of the placeholder passed in the [arg.name](#func.msg.set_arg.args.arg.name) argument found in the template.

@@

::: { #func.msg.glue.args.msg_template .sidebar }
  - **msg_template:** Any object coercible to a character vector containing at least one message template element, i.e., a string (possibly multiline) containing at least one occurrence of a pattern specified by the [arg.name](#func.msg.glue.args.arg.name) argument.

@@

::: { #func.msg.glue.args.arg.name .sidebar }
  - **arg.name:** Substring (pattern) to replace all occurrences found in the message template passed in the [msg_template](#func.msg.glue.args.msg_template) argument with the value specified in the [arg](#func.msg.glue.args.arg) argument.

::: { #func.msg.glue.args.arg .sidebar }
  - **arg:** Value to replace all occurrences of the pattern specified by the [arg.name](#func.msg.glue.args.arg.name) argument in the message template passed in the [msg_template](#func.msg.glue.args.msg_template) argument.

@@

This function internally calls the [stringr::str_glue](https://www.rdocumentation.org/packages/stringr/versions/1.5.0/topics/str_glue) `R` function to format the character vector returned by the (also called internally) [msg.set_arg](#func.msg.set_arg) function described above.

@@

A [glue::glue](https://glue.tidyverse.org/reference/glue.html) object created from the character vector returned by the internally called [msg.set_arg](#func.msg.set_arg) function.
